Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-06 manuscript.Rmd
mean travel time variability

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE)) %>%
  mutate(ifelse((year == 2017 && month == 1 && week %in% c(3, 4)), 1, 0))

# travel_time_sf[11122:11676, "march_inaug"] = 1
#entries 11122 to 11676
```

>>>>

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE),
  			 march_inaug = ifelse((year == 2017 & month == 1 & week %in% c(3, 4)), 1, 0))
```
